Data Analysis Methods for the Detection of the Epoch of Reionization

### 2017-11-27 PAPER.tex
-edited first pass of method #2 section

The second method we describe here... \cc{Danny and Matt's section}

\cc{refer back to Equations \eqref{eq:Pin} and \eqref{eq:sigloss} and explain why the subtraction term is removed}

\cc{also state at the end that the rest of the analysis uses method \#1 instead of \#2...}

>>>>

One of the main difficulties in defining a signal loss procedure is in the interpretation of the injection procedure `output'. Small differences in approaches were found to cause large differences in the final answer. \cc{but aren't we arguing the opposite - that they yield similar answers?}

For Method \#1, we used $P_{out}$ as the output of interest. For that method, we had asked the question ``What is the input power associated with an excess similar in amplitude to the data power spectrum?" For this second method, we rephrase the question to: ``At what point would an injected signal be detectable at significant levels?". Instead of looking at $P_{out}$, we now use $P_{r}$, the weighted power spectrum of the data plus signal, as the output of interest.

This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}. In the 2D space relating total $P_r$ to injected $P_{in}$, very small injected levels begin at the level equivalent of no injection (i.e. data only). \cc{this next sentence does not make sense} As $P_{in}$ increases, the signal loss transfer curve approaches the power level of the data it does not dominate the covariance but still contributes enough to suppressing itself. Above some level the injected signal is clearly detectable.

One difference in this method is that we are exclusively asking about signals detectable \emph{above} the level of the observed data. Thus it is explicitly limited to placing an upper limit, even if in some $k$-modes one has actual detections above the noise.  This might be seen as more conservative, however, a similar assumption has already been made when choosing to down-weight the data using itself. In such a down-weighting step, one has assumed that significant excess power is associated with a foreground residual. We note that a high SNR detection will require a different method, but we show this one to... \cc{fill in..}

Formally we can express our test as: ``What is the $P_{in}$ such that
\begin{equation}
P_{r} > P_{x} \Lambda,
\end{equation}  
where $\Lambda$ represents a choice of threshold.'' Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance. One way to interpret this test for the two distributions is to compute the probability that the two distributions are not\footnote{i.e. the null test} the same.

 \begin{equation}
\Prob(P_{in})  =  1 -  \int_{r=x} \Prob(P_x) \Prob(P_r,P_{in}) dr
 \end{equation}
 where $\Prob(P_x)$ is the probability of obtaining the power spectrum $P_x$ found via bootstrapping and $\Prob(P_r,P_{in})$ is the probability of obtaining the summed power spectrum $P_r$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.

Probability vs. injection level is shown in Figure \ref{fig:Prob_vs_Pin}. At low injection levels the variation between $x$ and $r$ is such that the null test is ruled out to within $20$\%. This is the level expected from two distributions with $\sim$10 effective samples. \dcj{checked with a little python test but needs a cite} As the injected signal approaches the level of the data, the probability of null rejection rises steeply.

Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis. As can be seen in Figure \ref{fig:Pr_vs_Pin}, the difference between $80$ and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out. We can also see that the probability does not perfectly converge at high injected power levels. \cc{why?} Rather than insist on a rejection at the $99$th percent level, we compromise at $95$\% \dcj{Matt, put in actual value here}.

The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Method \#1), using this second signal loss method, are shown in Figure \ref{fig:cc_vs_mk} next to the limits from Method \#1. \dcj{Hopefully they are similar!} In the rest of this paper, we use Method \#1 \cc{why?}.
